---
title       : Predicting Diamond Price 
subtitle    : Application of RandomForest
author      : Yunfeng Xi
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data Summary
```{r}
library(ggplot2)
data(diamonds)
str(diamonds)
```
---

---
## Exploratory Data Analysis
As an example, we plot `price` as function of `carat` and `cut`. 
```{r, echo=FALSE}
ggplot(diamonds, aes(carat, price, colour = cut)) +
  geom_point() + theme(legend.position = "top")
```
---

---
## RandomForest
* To expedite the prediction, 1000 samples are subsetted randomly from original about 50000 observations.
```{r, eval=FALSE}
library(caret)
library(randomForest)
diamonds <- diamonds[sample(nrow(diamonds), 1000, replace=FALSE), ]
modFit <- randomForest(price~., data=diamonds)
```
* User's input is recorded and formed into a one-row data frame `urDiamond`. 
* The price of diamond described by this data frame can be predicted with `predict()`.
```{r, eval=FALSE}
price <- predict(modFit, urDiamond)
```
---

---
## Acknowledges
* This app is built with `shiny` package. The `server.R`, `ui.R` and supporting files are
  in this [repo](https://github.com/arendale/DataProduct).
* This app is published on [shinyapp](http://arendale.shinyapps.io/DataProduct/).
